---
title: "Workmarket Challange"
output: html_document
---



I have picked first two challanges.

<b> 1. Counting Vitae</b>  

Take the plaintext version of your resume (or linkedin profile) and create a bar chart of character frequency. (Bonus: programmatically strip out punctuation and whitespace.)

```{r}
A<-"~/Desktop/Punam Katariya Resume.txt"
con<-file(A,open="r")
line<-readLines(con)
close(con)
length(line)
```

clean it up.

```{r,warning=FALSE}
txt<-tolower(unlist(strsplit(line,split="")))
txt1<-na.omit(txt)
chr_txt<-grep("[a-z]",txt1)
chr_str<-txt1[chr_txt]
tab<-table(chr_str)
```

Fun part plotting :)

```{r, echo=FALSE}
barplot(tab,main="My Resume Character Frequency Graph",col="blue")
```

I guess ggplot does make it look better.

```{r,echo=FALSE}
library(ggplot2)
ggplot(as.data.frame(tab),aes(x=chr_str,y=Freq))+
geom_bar(stat="identity",fill="Salmon")+xlab("Character")+
ggtitle("My Resume Character Frequency Graph\n") +
theme(panel.background=element_rect(fill="lightblue"))
```

<b> 2. Friendly Competition</b>

Here’s a list of all open jobs for the City of New York. <a> https://data.cityofnewyork.us/Business/NYC-Jobs/kpav-sd4t </a>

Determine:

1. Who has the most openings?

```{r}
library(knitr)
ny_jobs<-read.csv("NYC_Jobs.csv")
names(ny_jobs)
jobs<-ny_jobs[,c(2,4)]
depart_jobs<-unique(head(jobs[rev(order(jobs$X..Of.Positions)),],10))
kable(depart_jobs, format="markdown")
```


2. Which departments have the highest and the lowest paying positions (based on current job openings)?


```{r}
ny_jobs$salary_mean<-round(((ny_jobs$Salary.Range.From+ny_jobs$Salary.Range.To)/2),digits=0)  
newdf<-ny_jobs[,c(2,5,11,27)]

levels(newdf$Salary.Frequency) <- c(1, 52*5, 52*40)
newdf$Salary <- as.numeric(as.character(newdf$Salary.Frequency))*newdf$salary_mean
levels(newdf$Salary.Frequency) <- c("Annual", "Daily", "Hourly")

higest_pay<-unique(head(newdf[rev(order(newdf$Salary)),],10))
lowest_pay<-tail(newdf[rev(order(newdf$Salary)),],10)
kable(higest_pay,format="markdown") # Highest pay
kable(lowest_pay,format="markdown") # Lowest Pay
```


- DEPT OF HEALTH/MENTAL HYGIENE pays highest salary to Deputy Chief City Medical Examine position 
- DEPARTMENT OF FINANCE pays lowest wage to many intern and analyst positions


3. Which jobs do you think are the hardest to fill? (What makes you say that?)


```{r}
long_post<-ny_jobs[,c(2,5,23,25)]
long_post$newtime<-as.numeric(difftime(strptime(paste(long_post[,3]),"%m/%d/%Y %H:%M:%S"),
                    strptime(paste(long_post[,4]),"%m/%d/%Y %H:%M:%S")),units="mins") 

most_difficult<-head(long_post[order(long_post$newtime),],5)
kable(most_difficult,format="markdown")
```


Most difficult job to fill is waiver analyst from ADMIN FOR CHILDREN'S SVCS agency. The logic is the longest period this job was posted and updated which is -714180 minutes (11903 hours or 496 days). That makes it hardest to fill this position.

